HTW E1 Testing

### 2024-03-16 Analysis/combo_test.qmd
control for train models and figures

>>>>

d <- d |> 
    mutate(trainCon=case_when(
    bandOrder=="Original" ~ "800",
    bandOrder=="Reverse" ~ "600",
    TRUE ~ NA_character_
    ), trainCon=as.numeric(trainCon))

nbins=5
train <-  d |> filter(expMode2=="Train") |> group_by(id,condit,fb,bandOrder, vb) |> 
    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
train_max <- train |> filter(Trial_Bin == nbins, bandInt==trainCon)
train_avg <- train_max |> group_by(id,condit,fb,bandOrder) |> summarise(train_end = mean(dist))
train_avg2 <- train_max |> select(id,condit,fb,bandOrder,expMode2,vb,bandInt,dist,vx)

test2 <- d |> filter(expMode2=="Test") |> 
  select(id,condit,fb,bandOrder,expMode2,vb,bandInt,dist,vx) |> 
  rbind(train_avg2) |>
  left_join(train_avg, by=c("id","condit", "fb", "bandOrder"))

test <- d |> filter(expMode2=="Test") |> left_join(train_avg, by=c("id","condit", "fb", "bandOrder")) |>
  select(id,condit,bandType,bandInt,vb,vx,dist,train_end,fb,bandOrder)

```{r}
ltest|> group_by(id,condit) |> pivot_longer(c("dist","train_end"),names_to="var",values_to="value") |> 
  ggplot(aes(x=var,y=value, fill=condit)) + stat_bar + facet_wrap(~var)

test2 |> ggplot(aes(x=bandInt,y=dist,fill=expMode2)) + stat_bar + facet_wrap(~condit+fb+bandOrder)

test2 |> mutate(train_end_q = ntile(train_end,4)) |>  
  ggplot(aes(x=bandInt,y=dist,fill=expMode2)) + stat_bar + facet_wrap(~condit+train_end_q+bandOrder)

test2 |> mutate(train_end_q = ntile(train_end,4)) |>  
  ggplot(aes(x=condit,y=dist,fill=vb)) + stat_bar + 
  facet_wrap(~expMode2+train_end_q+bandOrder,scales="free")

test2 |> mutate(train_end_q = ntile(train_end,4)) |>  
  ggplot(aes(x=vb,y=dist,fill=condit)) + stat_bar + 
  facet_wrap(~expMode2+train_end_q+bandOrder,scales="free")

test2 |> mutate(train_end_q = ntile(train_end,4)) |>  
  ggplot(aes(x=train_end_q,y=dist,fill=condit)) + stat_bar + 
  facet_wrap(~expMode2+vb+bandOrder,scales="free")

test |> ggplot(aes(x=train_end,y=dist,fill=condit)) + 
  stat_summary(geom = "line", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
    facet_wrap(~vb) +
  labs(x="Band", y="Deviation From Target")

test |> filter(bandType=="Extrapolation") |>
  ggplot(aes(x=train_end,y=dist,fill=condit,col=condit)) + 
  #geom_point() +
  geom_smooth(method="loess") +
    facet_nested_wrap(~bandOrder+vb+fb) +
  labs(x="Band", y="Deviation From Target")

test |> filter(bandType=="Extrapolation") |>
  ggplot(aes(x=train_end,y=dist,fill=condit,col=condit)) + 
  #geom_point() +
  geom_smooth() +
    facet_nested_wrap(~bandOrder+vb+fb) +
  labs(x="Band", y="Deviation From Target")

test |> filter(bandType=="Extrapolation") |>
  ggplot(aes(x=train_end,y=dist,fill=condit,col=condit)) + 
  #geom_point() +
  geom_smooth(method="lm") +
    facet_nested_wrap(~bandOrder+vb) +
  labs(x="Band", y="Deviation From Target")

# create quartiles for train_end
test |> group_by(condit,vb,fb,bandOrder) |>  filter(bandType=="Extrapolation") |>
  mutate(train_end_q = ntile(train_end,4)) |> 
  ggplot(aes(x=train_end_q,y=dist,fill=condit)) + 
 stat_bar + 
    ggh4x::facet_wrap2(bandOrder~vb~fb) +
  labs(x="Band", y="Deviation From Target")

test |> group_by(condit,vb,fb,bandOrder) |>  #filter(bandType=="Extrapolation") |>
  mutate(train_end_q = ntile(train_end,4)) |> 
  ggplot(aes(x=condit,y=vx,fill=vb)) +
  stat_bar + 
    ggh4x::facet_wrap2(~train_end_q+bandOrder+fb)

### 2024-03-16 Analysis/e1.qmd
control for train models and figures

walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
e1 <- readRDS(here("data/e1_08-21-23.rds")) 
e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
testE1 <- e1 |> filter(expMode2 == "Test")
nbins=5
trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
```

>>>>

walk(c("brms","dplyr","bayestestR"), conflict_prefer_all, quiet = TRUE)
walk(c("Display_Functions","org_functions"), ~ source(here::here(paste0("Functions/", .x, ".R"))))
e1 <- readRDS(here("data/e1_08-21-23.rds")) 
e1Sbjs <- e1 |> group_by(id,condit) |> summarise(n=n())
testE1 <- e1 |> filter(expMode2 == "Test")
nbins=5
trainE1 <-  e1 |> filter(expMode2=="Train") |> group_by(id,condit, vb) |> 
    mutate(Trial_Bin = cut( gt.train, breaks = seq(1, max(gt.train),length.out=nbins+1),include.lowest = TRUE, labels=FALSE)) 
trainE1_max <- trainE1 |> filter(Trial_Bin == nbins, bandInt==800)
trainE1_avg <- trainE1_max |> group_by(id,condit) |> summarise(avg = mean(dist))
```

### 2024-03-16 Analysis/e1_test.qmd
control for train models and figures

>>>>

```{r}

testE1 |> group_by(id,condit) |> pivot_longer(c("dist","train_end"),names_to="var",values_to="value") |> 
  ggplot(aes(x=var,y=value, fill=condit)) + stat_bar + facet_wrap(~var)

testE1 |> ggplot(aes(x=train_end,y=dist,fill=condit)) + 
  stat_summary(geom = "line", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
    facet_wrap(~vb) +
  labs(x="Band", y="Deviation From Target")

testE1 |> ggplot(aes(x=train_end,y=dist,fill=condit,col=condit)) + 
  #geom_point() +
  geom_smooth(method="loess") +
    facet_wrap(~vb) +
  labs(x="Band", y="Deviation From Target")

# create quartiles for train_end
testE1 |> group_by(condit,vb) |> 
  mutate(train_end_q = ntile(train_end,6)) |> 
  ggplot(aes(x=train_end_q,y=dist,fill=condit)) + 
 stat_bar + 
    facet_wrap(~vb) +
  labs(x="Band", y="Deviation From Target")
